% MIT License
% 
% Copyright (c) 2022 cgsdfc
% 
% Permission is hereby granted, free of charge, to any person obtaining a copy
% of this software and associated documentation files (the "Software"), to deal
% in the Software without restriction, including without limitation the rights
% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
% copies of the Software, and to permit persons to whom the Software is
% furnished to do so, subject to the following conditions:
% 
% The above copyright notice and this permission notice shall be included in all
% copies or substantial portions of the Software.
% 
% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
% SOFTWARE.

\documentclass[runningheads]{llncs}

\usepackage{caption} % change the font size of figure captions.
\captionsetup[figure]{font=small}
\usepackage{graphicx}
\usepackage{array}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{float}
\usepackage{subcaption}
\usepackage{color}

\renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
    \title{Automatic Evaluation of Generative Dialogue Systems: An Empirical Study}
    \titlerunning{Automatic Evaluation of Generative Dialogue Systems}
    \author{Cong Feng \and Wenge Rong \and Jianxin Yang \and Haodong Yang \and \\Yuanxin Ouyang \and Zhang Xiong}
    \authorrunning{Feng et al.}
    \institute{
    School of Computer Science and Engineering, Beihang University, Beijing, China
    \email{\{congfeng, w.rong, yjx17, yhd125, oyyx, xiongz\}@buaa.edu.cn}
    }

    \maketitle

    % --------------------------- %
    % --------- Abstract -------- %
    % --------------------------- %
    \begin{abstract}
        Evaluating generative dialogue systems with automatic metrics is a challenging task. It has been shown that word-overlap metrics such as BLEU and word-embedding metrics do not correlate well with human judgments. Furthermore, regardless of the correlation with human judgments, the scores of these metrics do not correlate well with others, which means fine-tuning a dialogue system on one set of metrics may yield inconsistency when testing with another set of metrics. This infeasibility again adds to the ineffectiveness of evaluation dialogue systems. To the end of utilizing metrics at their best, in this research, we offer several pragmatic suggestions on the use of automatic metrics to avoid the issue of metric inconsistency by empirically evaluating a set of automatic evaluation metrics.
        \keywords{Automatic Evaluation Metrics, Dialogue Response Generation, Chatbot}
    \end{abstract}

    % ----------------------------------- %
    % ---------- Introduction ----------- %
    % ----------------------------------- %
    \section{Introduction}
    Recently chat-oriented dialogue systems have seen a boom in the community. These systems are trained to make an appropriate response given a conversational context and can be applied to various applications. One of the fundamental techniques in such dialogue systems is the generative model, which can learn language patterns and extract knowledge from the corpus in an unsupervised manner. The research community has made steady progress with the generative models and one of the most widely used techniques is the Seq2Seq model \cite{Seq2Seq}. Though generative models have shown promising results, there exists one essential challenge. They are inclined to give meaningless responses to the questions, e.g., \textit{I don't know}, thereby making their evaluation remain an open problem \cite{HowNot}.

    Currently, most generative dialogue systems are evaluated by borrowing automatic metrics from other tasks, e.g., machine translation, such as the BLEU \cite{BLEU}, METEOR \cite{METEOR} etc. However, the correlations between these borrowed metrics and human judgments were unclear and researchers generally fell back to human evaluation for better accuracy and reliability \cite{VHRED,Shang}. It is found that those metrics only correlated weakly with human judgments on the non-technical Twitter corpus and not at all on the technical Ubuntu Dialogue Corpus \cite{HowNot}, which calls for new automatic metrics that are more relevant to human judgments.

    In this paper, we followed the previous work and further investigated the behaviors of automatic metrics without human judgments. We analyzed both system-level and example-level scores to find out possible correlations among different metrics. In particular, we drew samples from the example-level scores of different metrics and analyze the pairwise correlation of these samples. It is found that some pairs of samples have a high correlation, while other pairs show a much lower one.

    Following these observations, we further clustered the metrics based on the pairwise correlations of their corresponding samples. The results show that similar metrics tend to cluster together, indicating a high pairwise correlation within the same group. According to the experiment results, it is argued that the scores given by dissimilar metrics have the risk of high inconsistency, which is yet another pitfall of using automatic metrics. Therefore, it is strongly recommended to choose consistent metrics for ease of comparison across different settings.

    % ----------------------------------- %
    % ----------- Related Work ---------- %
    % ----------------------------------- %
    \section{Related Work}
    In dialogue response generation, to address the issue of low metric-human correlation, various semantic-based methods have been proposed. For example, the ADEM metric proposed models the human judgments with a feed-forward neural network \cite{ADEM}. The RUBER metric takes an asymmetric approach w.r.t the response-context pair and response-reference pair, where the former is modeled by a neural network and the latter is measured by an embedding-based metric. They combined two scores with various heuristics and achieved improvements on a Chinese corpus \cite{RUBER}. In brief, correlation with human judgments has been the supervised signal guiding the evolution of automatic metrics.

    Other popular metrics include perplexity, which is generally used to evaluate statistical language models. Vinyals et al. revealed that their Seq2Seq dialogue model achieved a much lower perplexity than the n-gram baseline, but they also admitted the drawbacks of using such a metric \cite{GoogleChatbot}. Serban et al. also used perplexity to evaluate their models \cite{HRED}, along with other metrics. However, they were also not clear about how well these metrics accounted for the grammatical correctness and semantic coherence of the responses.

    Generally, automatic metrics have been constantly doubted for their capability to reflect human judgments. In one of the earliest attempts at the response generation problem, Ritter et al. made an initial examination of the suitability of BLEU to this field leveraging the human data they collected \cite{Ritter11}. They found that the BLEU scores were very low even on the system level and the correlation was modest. Similarly, Shang et al. also argued that BLEU did not apply as the reasonable responses evaluation \cite{Shang}.

    An extensive study of metric-human correlation was conducted by Liu et al. \cite{HowNot}. It was revealed that although these metrics could distinguish state-of-art models from baseline models, none of them correlated highly with human scores. Their work has left us with two questions: 1) How can we improve the metric-human correlation? 2) Why do the existing metrics correlate badly with human judgments? Previous works that proposed enhanced metrics endeavored to answer the first question, while we try to shed some light on the second one. In particular, we are curious about what can we learn when scores from different metrics are put together and compared across various settings.

    % ----------------------------------- %
    % --------- Experiment Setup -------- %
    % ----------------------------------- %
    \section{Experiment Configuration}
    Our experiment essentially involves training multiple generative models on multiple datasets and then measuring their performances with various automatic metrics. As stated, our study does not involve human evaluation. We also do not consider retrieval models as we mainly focus on generative models. Due to time and resource constraints, we limit our scope to three commonly used models and three datasets.

    % ------------------------- %
    % --------- Metrics ------- %
    % ------------------------- %
    \subsection{Metrics}
    Here is a list of popular metrics used in dialogue response evaluation included in this research.

    1) BLEU \cite{BLEU} is a classical metric for machine translation that reports a high correlation with human scores on the system level. It owes the quality of a hypothesis to its similarity to multiple references. It computes the geometric mean of consecutive orders of n-gram precision, multiplied by a brevity penalty.

    2) METEOR \cite{METEOR} is a metric proposed to address several issues with BLEU. It applies multiple stages of unigram matching to the hypothesis and reference, each using a different criterion, such as exact matching, WordNet synonyms, and paraphrases. An alignment is then created from these unigram matches. The score is based on the F1 of the alignment and a penalty to shorter matches.

    3) ROUGE \cite{ROUGE} is a family of metrics for automatic summarization. It is based on the F1 score and can integrate different counting units, e.g., n-gram statistics and the longest common subsequence.

    4) Embedding Average is a metric based on word embedding, a distributed approach to the meaning of words \cite{word2vec}. The embedding of a sentence is defined as the average of the embeddings of its composing words. The similarity of two sentences is then simply defined as the cosine of the corresponding vectors.

    5) Vector Extrema \cite{Vector_Extrema} composes the sentence embedding by taking the most extreme value (either maximum or minimum) along each dimension from its constitutive words. The intuition is that in the embedding space, common words like function words are pulled towards the origin as they appear in the context of many different words, while informative words are pushed away from the origin in either positive or negative directions since they tend to appear in more specific contexts.

    6) Greedy Matching \cite{GreedyAndOptimal} is an embedding-based method without calculating a sentence vector. Instead, two sentences under comparison are treated as a weighted bipartite graph, taking their words as nodes and the embedding cosine of two words $\cos(w, w')$ as the edge weight. The metric is based on a greedy method to solve the optimal matching problem on the weighted graph:
    \begin{align}
        G(r, \hat{r}) = \frac{
        \sum_{w \in r} \max_{\hat{w} \in \hat{r}} \cos(e_w, e_{\hat{w}})
        }{ |r| } \\
        \textit{Greedy-Matching} = \frac{
        G(r, \hat{r}) + G(\hat{r}, r)
        }{2}
    \end{align}
    where $r$ and $\hat{r}$ are the reference and response, respectively.

    7) ADEM \cite{ADEM} is an approach based on a concise neural network. The model first embeds a context $c$, response $\hat{r}$, and reference $r$ into a low-rank vector space and then predicts the human score with a linear combination of the input features:
    \begin{align}
        s(c, r, \hat{r}) = \frac{(c^T M \hat{r} + r^T N \hat{r} - \alpha)}{\beta}
    \end{align}
    $M, N$ are learnable parameters of the network, and $\alpha, \beta$ are constants to normalize the output to a five-point score. The model is trained on a human-annotated conversation corpus to minimize the squared error with L2 regularization:
    \begin{align}
        L = \sum_{i=1}^{K} (s_i - h_i)^2 + \gamma \left\| \theta \right\| _2
    \end{align}
    where $K$ is the number of samples in a batch. $s_i$ and $h_i$ are the model prediction and the human score, respectively. $\theta$ is the parameters of the network and $\gamma$ is the regularization factor.

    8) Distinct-N \cite{MMI} measures the rate of unique n-grams in a sentence. For a sentence, it is the number of unique n-grams divided by the total number of n-grams. It is a token-level measurement of the diversity of response.

    % ------------------------- %
    % --------- Models -------- %
    % ------------------------- %
    \subsection{Models}
    In our research, three representative models from \cite{VHRED} are selected, namely LSTM, HRED, and VHRED. LSTM is a simple model based on the Long Short-Term Memory \cite{LSTM}. HRED extends the standard Seq2Seq framework by using a hierarchical encoder. VHRED is an extension to HRED that injects randomness into the decoder to achieve higher diversity. As such, they form a hierarchy of architectural sophistication and are ideal baselines of generative models.

    1) The LSTM model is a simple generative model with a single RNN acting as both an encoder and a decoder. Note that the generative LSTM model is not autoregressive as the output of the previous time step does not become the input of the current time step.

    2) The HRED model \cite{hred-qs,HRED} features a hierarchical encoding mechanism that takes into account the structure of dialogues. It first encodes each sentence with the \emph{utterance encoder} into a fixed-length utterance vector $e_u$. Then, the utterance vectors are processed iteratively by the \emph{context encoder} to produce a fixed-length context vector $e_d$. Finally, the \emph{utterance decoder} takes the context vector and generates the next utterance of the dialogue.

    3) The VHRED model \cite{VHRED} extends the HRED model with a variational inference mechanism. Essentially, VHRED injects into the utterance decoder random variables that are sampled from a high-dimension normal distribution, the parameters of which are conditioned on the context vector $e_d$.

    The configurations for different model components are shown in Table \ref{tab:model_config}. We used Adam \cite{AdamOpt} as our optimizer and applied gradient clipping with a threshold of 1. The learning rate was set to 0.0002 on the Ubuntu corpus and 0.0002 on the others. All the models were trained on an Nvidia GTX for at least one week. We used random sampling when testing.
    \input{data/model_config.tex}

    % --------------------------- %
    % --------- Datasets -------- %
    % --------------------------- %
    \subsection{Datasets}
    In this research, we select three commonly used datasets, the statistics of which are listed in table \ref{tab:dataset_stats}. These datasets represent three common domains in the literature, namely technical support, movie subtitles, and online forums.
    \input{data/dataset_stats.tex}

    1) The Ubuntu Dialogue Corpus \cite{ubuntu_corpus} is a large-scale multi-turn dyadic technical corpus collected from the Ubuntu channel of an IRC network\footnote{\url{https://irclogs.ubuntu.com/}}. It contains a lot of technical symbols, such as filesystem paths, commands, and URLs.

    2) The OpenSubtitles dataset \cite{opensub} is an enormous corpus of movie subtitles. It is collected by the OPUS project \cite{OPUS} from the opensubtitles website\footnote{\url{http://www.opensubtitles.org}}. Typically, two consecutive utterances are treated as a context-response pair, as in \cite{GoogleChatbot,MMI}.

    3) LSDSCC \cite{LSDSCC} is a domain-specific conversation corpus collected from the movie subreddit of the Reddit forum\footnote{\url{https://www.reddit.com/r/datasets}}. It is believed that a more specific domain can help avoid generating universal responses \cite{LSDSCC}.

    % ------------------------------------- %
    % --------- Experimental Study -------- %
    % ------------------------------------- %
    \section{Experimental Study}
    \subsection{System-Level Scores}
    We first measured the system-level scores for all settings, shown in Table \ref{tab:system_scores}. The system-level score reflects the average performance of a model trained on a dataset. For metrics that do not have an explicit system-level definition, we took the arithmetic average of their example-level scores.
    \input{data/system_scores.tex}

    The system-level scores of different metrics look quite consistent in terms of the best-performing model on a certain dataset. On LSDSCC, for example, the HRED model beats all the other models on all but one metric, while on OpenSubtitles, the VHRED model wins the best of most of the metrics. The system-level score seems to be able to distinguish state-of-the-art models from baselines since most of the metrics agree on which model is the best.

    However, the consistency among the metrics does not necessarily lead to a high correlation with human judgment, as shown in \cite{HowNot}. Moreover, since the system-level score is calculated by accumulating over the example-level scores, the inconsistency on the example level may be hidden away. To reveal the possible inconsistency, we performed analyses on the example-level scores.

    \subsection{Example-Level Scores}
    On the example level, a matrix $M \in R^{N \times M}$ is calculated for each model instance, where $N$ is the number of examples and $M$ is the number of metrics. Each row $r_i$ of the matrix is the scores of all metrics for an example $e_i$, while each column $c_j$ is the values of a metric $s_j$ computed for all examples. All the metrics share the same set of examples within a matrix. Thus, the correlation of any two columns $c_i, c_j$ can be understood as to how much the corresponding metrics $s_i, s_j$ agree on their shared examples. We compute the pairwise correlations of the metrics and highlight the degree of correlation with heatmaps, as shown in Fig. \ref{fig:corr_heatmap}. We used Pearson's r and all the results are statistically significant.

    \input{data/heatmap.tex}

    Each subfigure in Fig. \ref{fig:corr_heatmap} was plotted from the correlation matrix for a model instance. The color of the cells represents the degree of correlation between the row and column labels, with red, blue, and white stand for positive, negative, and zero correlation, respectively. One can observe red regions divided by white or blue lines from these plots, showing signs of clustering.

    To better observe the agreement and disagreement among the metrics, we applied hierarchical clustering to the metrics based on their correlations, and the results are shown in Fig. \ref{fig:hierarchy}. A hierarchical clustering algorithm starts with a forest of nodes and iteratively merges them into larger clusters until the root cluster is created. We used the following node-level distance $\textit{dist}(\cdot, \cdot)$ and cluster-level distance $d(\cdot, \cdot)$:
    \begin{align}
        \textit{dist}(i, j) &= 1 - \textit{corr}(i, j) \\
        d(u, v) &= \frac{\sum_{i,j}\textit{dist}(i, j)}{|u| \cdot |v|}
    \end{align}
    where $i$ and $j$ are points in cluster $u$ and $v$, respectively. $|u|$ and $|v|$ are the cardinalities of cluster $u$ and $v$, respectively\footnote{This is also known as the average method.}. Again the correlation is based on Pearson's r.
    \input{data/hierarchy.tex}

    From Fig. \ref{fig:hierarchy}, we observe a hierarchy of agreement among different metrics. The clusters created in the earlier iterations appear closer to the leaves of the tree, which indicates higher pairwise correlations or stronger inter-metric agreement. As a cluster grows larger, its children become more loosely connected. It is interesting to find that the dendrograms in Fig. \ref{fig:hierarchy} share some regular structure, which has an observable correspondence to the category of the metrics. Across all the settings, we generally observe these independent clusters, named after the shared category or representative element:

    1) Word-Overlap: a large cluster that contains many subclusters formed by different word-overlap metrics, such as BLEU, ROUGE, and METEOR.

    2) Word-Embedding: a small cluster that contains Vector-Average, Vector-Extrema, and Greedy-Matching.

    3) ADEM: a standalone cluster formed by ADEM.

    4) Distinct-1: a metric that might belong to some cluster or become a standalone cluster depending on the dataset involved.

    5) Distinct-2 and \#words: a generally observable cluster.

    Those clusters confirm our hypothesis on the inconsistency among different metrics. Luckily, there are still some forms of agreement that the same cluster of metrics can reach. Unfortunately, the exact reasons why the clusters are formed this way are unclear to us. Although our experiments have a simple procedure, it should be noted that the mechanism behind each step has a complex nature. For example, the dialogue datasets are intrinsically very diverse and the way the generative models work is not well-understood. Besides, it is also unclear how these metrics reflect the desirable properties of a response. Hence we can only conclude that similar metrics tend to have consistent results on the example level. The similarity of metrics generally refers to their mechanisms, such as the way to extract overlap units or derive semantics from an utterance, or the way to combine different components.

    Specifically, we find that metrics based on word overlap tend to have high pairwise correlations since they all make use of the n-gram statistics somehow. We also find that ADEM does not correlate well with all the other metrics since it has a much higher correlation with human judgment while other metrics do not.

    \subsection{Qualitative Analysis}
    \input{data/example/OpenSubtitles.tex}
    Table \ref{tab:Example_OpenSubtitles} serves as an example of the inter-metrics inconsistency. The response from HRED mentions ``her room'', which is relevant to the subject ``she'' in the context and the verb ``starts'' matches the ``start'' in the reference. The response from VHRED does not share any token with the context or reference, but it remarks on the event mentioned by the context so it is quite a reasonable one.

    All three responses share no n-grams with either the context or the reference in terms of exact matching. Thus, all the word-overlap metrics yield a zero value. However, all the word-embedding metrics give non-zero values, making them incompatible with the word-overlap metrics.

    In terms of semantic relevance, the responses from both HRED and VHRED are somehow related to the topic of the dialogue, while the response from LSTM looks grammatically incomplete. One will mostly agree that the responses from HRED and VHRED are equally better than that from LSTM. Nonetheless, the ranks given by the word-embedding metrics do not agree with our manual inspection. For example, they all give higher scores to LSTM than HRED.

    \section{Conclusion and Future Work}
    In this paper, we followed the work of \cite{HowNot} and try to understand the reasons behind low metric-human correlations. We investigated the system-level scores and leveraged statistical analyses to reveal the inter-metrics correlation on the example level. Our study shows a high consistency of metrics on the system level, as shown by others \cite{HowNot,VHRED,GoogleChatbot}. We further show that on the example level, similar metrics tend to score the examples more consistently and the degree of correlations forms a hierarchical cluster.

    Intuitively, different metrics judge a dialogue from different angles, while human beings judge it from a quite comprehensive perspective. This might explain why the metrics do not correlate well with human judgments. Our discovery of the example-level correlation-based hierarchical clusterings of metrics is a novel contribution.

    Based on the observations, it is recommended to avoid using a set of metrics that have low pairwise correlations since that will make the example-level scores divergent and hard to explain. We also urge against the use of metrics that are known to have poor correlations with human judgments. In the future, we would like to look deeper into the mechanisms behind the metric-human correlations.

    \bibliographystyle{splncs04}
    \bibliography{reference}
\end{document}
